State of the Practice for Lattice Boltzmann Method Software

### 2022-10-06 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
Edits to SOP for LBM to update Table 11 to show top two packages for each quality

\begin{table}[ht!]
	\begin{center}
		\begin{tabular}{ p{3cm}p{3cm}p{2.1cm}p{2.1cm}p{2.1cm}p{2.1cm} }
			\toprule
			Quality & Ranked 1st & Ranked 2nd & Ranked 3rd & Ranked 4th & Ranked
			5th\\
			\midrule
			Installability & ESPResSo, MechSys, OpenLB & & & DL\_MESO (LBE),
			Palabos, Sailfish &\\
			\addlinespace[0.4cm]
			\pbox{3.0cm}{Surface Correctness \\ and Verifiability} & Ludwig &
			Musubi, pyLBM & & ESPResSo, waLBerla &\\
			\addlinespace[0.4cm]
			Surface Reliability & Musubi, DL\_MESO (LBE), ESPResSo, laboetie*, lettuce, LUMA, MechSys, OpenLB, Palabos, pyLBM, TCLB, & & & & \\
			\addlinespace[0.4cm]
			Surface Robustness & DL\_MESO, ESPResSo, \esp, laboetie*, LB2D-Prime*, LB3D-Prime*, lettuce, LIMBES*, Ludwig, LUMA, MechSys, OpenLB, Palabos, pyLBM, Sailfish, SunlightLB*, TCLB, waLBerla & & & & \\
			\addlinespace[0.4cm]
			Surface Usability & ESPResSo, laboetie*, Ludwig, OpenLB, Sailfish & & & & \\
			\addlinespace[0.4cm]
			Maintainability & ESPResSo, Ludwig, Palabos, waLBerla & & & & \esp \\
			\addlinespace[0.4cm]
			Reusability & ESPResSo, waLBerla & & \esp, HemeLB*, Musubi, OpenLB, Palabos, Sailfish & &\\
			\addlinespace[0.4cm]
			\pbox{3.0cm}{Surface \\Understandability} & LUMA & DL\_MESO (LBE), lettuce, Musubi, Palabos & & & \\
			\addlinespace[0.4cm]
			\pbox{3.0cm}{Visibility and \\Transparency} & Ludwig & ESPResSo, LUMA, Palabos & & & MP-LABS*\\
			\addlinespace[0.4cm]
			Overall Quality & ESPResSo & Ludwig & Palabos & LUMA & OpenLB \\
			\bottomrule
		\end{tabular}
		\caption{Top performers for each quality (all packages were alive at the
		time of measurement, except for those marked by an asterisk (*)) (Sorted
		by Order of Quality Measurement)}
		\label{topperformerstable}
	\end{center}
\end{table}

>>>>

\begin{table}[ht!]
	\begin{center}
		\begin{tabular}{ p{3cm}p{13cm} }
			\toprule
			Quality & Ranked 1st or 2nd\\
			\midrule
			Installability & ESPResSo, MechSys, OpenLB, DL\_MESO (LBE),
			Palabos, Sailfish\\
			\addlinespace[0.4cm]
			\pbox{3.0cm}{Surface Correctness \\ and Verifiability} & Ludwig,
			Musubi, pyLBM\\%, ESPResSo, waLBerla\\
			\addlinespace[0.4cm]
			Surface Reliability & Musubi, DL\_MESO (LBE), ESPResSo, laboetie*, lettuce, LUMA, MechSys, OpenLB, Palabos, pyLBM, TCLB\\
			\addlinespace[0.4cm]
			Surface Robustness & DL\_MESO, ESPResSo, \esp, laboetie*, LB2D-Prime*, LB3D-Prime*, lettuce, LIMBES*, Ludwig, LUMA, MechSys, OpenLB, Palabos, pyLBM, Sailfish, SunlightLB*, TCLB, waLBerla, Musubi\\
			\addlinespace[0.4cm]
			Surface Usability & ESPResSo, laboetie*, Ludwig, OpenLB, Sailfish, DL\_MESO, \esp LB2D-Prime*, LB3D, LUMA, TCLB\\
			\addlinespace[0.4cm]
			Maintainability & ESPResSo, Ludwig, Palabos, waLBerla, \esp, LUMA, MP-LABS, pyLBM, TCLB\\
			\addlinespace[0.4cm]
			Reusability & ESPResSo, waLBerla, \esp, HemeLB*, Musubi, OpenLB, Palabos, Sailfish\\
			\addlinespace[0.4cm]
			\pbox{3.0cm}{Surface \\Understandability} & LUMA, DL\_MESO (LBE), lettuce, Musubi, Palabos\\
			\addlinespace[0.4cm]
			\pbox{3.0cm}{Visibility and \\Transparency} & Ludwig, ESPResSo, LUMA, Palabos\\
			\addlinespace[0.4cm]
			Overall Quality & ESPResSo, Ludwig\\%, Palabos, LUMA, OpenLB\\
			\bottomrule
		\end{tabular}
		\caption{Top performers for each quality (all packages were alive at the
		time of measurement, except for those marked by an asterisk (*)) (Sorted
		by Order of Quality Measurement)}
		\label{topperformerstable}
	\end{center}
\end{table}
